Regional Inequalities and economic growth; cross section and times series analysis

### 2023-11-22 MSB104_GR_1_Final_Assignment_research_article.qmd
final update assignment 3

library(tidyverse)
library(tinytex)
library(dplyr)
library(ggplot2)
library(readxl)
library(magrittr)
library(vtable)
library(lubridate)
library(dineq)
library(huxtable)
library(plm)
```

@@

# Alternative functional forms and panel estimation

By exploring our previous estimates in the relationship between regional development on regional inequality we will estimate the log of GDP per capita in a liner regression model, defining the variables as new determinants on the effects in regional economic development using logarithim of GDP per capita.

Firstly, the data is devided into different subsets. Using France (x) as a binary value also called a dummy variable [@wooldridge2020].

Choosing France as a dummy variable amongst our group of countries could be justified based on several criteria. Firstly, France stands out as one of the largest economies in this group, both in terms of GDP and global economic influence. This distinction makes France a unique case compared to the smaller economies of Denmark, Portugal, Hungary, and Slovakia. Secondly, France's larger geographical area and population size provide different economic dynamics and complexities, which are not as pronounced in the smaller and more homogenous countries like Denmark, Portugal, Hungary, and Slovakia. Thirdly, France's economy is more diversified compared to the other countries listed, which might have more specialized or less varied economic structures. This diversity can lead to different patterns in wealth distribution and economic development. Lastly, France's policies, particularly in social welfare and economic regulation, and its larger domestic market, might influence economic outcomes differently than in the smaller economies, where external trade and different policy contexts play a more significant role.

## Part 3A Testing Development effects across subsets

To elucidate the differences between France and other countries, we employed various analytical methods including descriptive, regression, and comparative analyses. Descriptively, France exhibits a mean Gini coefficient of 0.06960, marginally higher than the 0.062308 average of the other countries, suggesting more pronounced economic inequality. Correspondingly, France's mean GDP per capita is also higher (2.750 compared to 1.743), indicating a higher level of economic development. This juxtaposition of heightened economic inequality and development in France raises intriguing questions, addressed further in our regression analysis.

In the regression analysis of France, the intercept is -0.034 with a statistically significant p-value below 0.001, indicating a non-zero intercept. More notably, the coefficient for the logarithm of GDP per capita stands at 0.110, with a p-value below 0.001, implying a significant increase in the Gini coefficient with rising GDP per capita. This suggests that higher GDP per capita correlates with greater income inequality. The R-squared value of 0.490 indicates that about 49% of the variance in the Gini coefficient is accounted for by GDP per capita, reflecting a strong model fit. This substantial correlation necessitates further investigation into the dynamics linking economic development with inequality in France.

## Part 3B Exploring Alternative Functional Forms

### **The cuznets cuve**

@@

```{r}
#| echo: false
#| output: false
# Logarithmic model
log_model <- lm(gini_n2 ~ log(GDP_per_capita), data = gini_filtered)

# Quadratic model
quad_model <- lm(gini_n2 ~ GDP_per_capita + I(GDP_per_capita^2), data = gini_filtered)

# Cubic model
cubic_model <- lm(gini_n2 ~ GDP_per_capita + I(GDP_per_capita^2) + I(GDP_per_capita^3), data = gini_filtered)

# Check the summary of each model
summary(log_model)
```

```{r}
summary(cubic_model)
```

```{r}
summary(quad_model)
```

@@

```{r}
#| echo: false
#| output: false
# Quadratic model

# Create a new data frame for plotting predicted values
plot_data <- data.frame(GDP_per_capita = seq(min(gini_filtered$GDP_per_capita), max(gini_filtered$GDP_per_capita), length.out = 250))
plot_data$gini_pred <- predict(quad_model, newdata = plot_data)

# Plotting
ggplot(gini_filtered, aes(x = GDP_per_capita, y = gini_n2)) +
  geom_point(alpha = 0.5) +  # Plot the actual data points
  geom_line(data = plot_data, aes(x = GDP_per_capita, y = gini_pred), color = 'blue') +  # Add the regression line
  labs(title = "Quadratic Model of GDP per Capita and Gini Coefficient",
       x = "GDP per Capita",
       y = "Gini Coefficient") +
  theme_minimal()
```

```{r}
#| echo: false
#| output: false
# Logarithmic model

# Create a new data frame for plotting predicted values
plot_data <- data.frame(GDP_per_capita = seq(min(gini_filtered$GDP_per_capita), max(gini_filtered$GDP_per_capita), length.out = 250))
plot_data$gini_pred <- predict(log_model, newdata = plot_data)

# Plotting
ggplot(gini_filtered, aes(x = GDP_per_capita, y = gini_n2)) +
  geom_point(alpha = 0.5) +  # Plot the actual data points
  geom_line(data = plot_data, aes(x = GDP_per_capita, y = gini_pred), color = 'red') +  # Add the regression line
  scale_x_log10() +  # Logarithmic scale for the x-axis
  labs(title = "Logarithmic Model of GDP per Capita and Gini Coefficient",
       x = "GDP per Capita (log scale)",
       y = "Gini Coefficient") +
  theme_minimal()
```

```{r}
#| echo: false
#| output: false
# Create a new data frame for plotting predicted values
plot_data <- data.frame(GDP_per_capita = seq(min(gini_filtered$GDP_per_capita), max(gini_filtered$GDP_per_capita), length.out = 250))
plot_data$gini_pred <- predict(cubic_model, newdata = plot_data)

# Plotting
ggplot(gini_filtered, aes(x = GDP_per_capita, y = gini_n2)) +
  geom_point(alpha = 0.5) +  # Plot the actual data points
  geom_line(data = plot_data, aes(x = GDP_per_capita, y = gini_pred), color = 'blue') +  # Add the regression line
  labs(title = "Cubic Model of GDP per Capita and Gini Coefficient",
       x = "GDP per Capita",
       y = "Gini Coefficient") +
  theme_minimal()
```

```{r}
#| echo: false
#| output: false
# Calculate residuals
residuals_quad <- gini_filtered$gini_n2 - predict(quad_model, gini_filtered)
residuals_cubic <- gini_filtered$gini_n2 - predict(cubic_model, gini_filtered)
```

```{r}
#| echo: false
#| output: false
# Create a dataframe for plotting residuals
residuals_data <- data.frame(GDP_per_capita = gini_filtered$GDP_per_capita, 
                             Residuals_Quad = residuals_quad, 
                             Residuals_Cubic = residuals_cubic)

# Plotting residuals
ggplot(residuals_data) +
  geom_line(aes(x = GDP_per_capita, y = Residuals_Quad, color = "Quadratic")) +
  geom_line(aes(x = GDP_per_capita, y = Residuals_Cubic, color = "Cubic")) +
  labs(title = "Comparison of Residuals",
       x = "GDP per Capita",
       y = "Residuals") +
  theme_minimal() +
  scale_color_manual(values = c("Quadratic" = "blue", "Cubic" = "red"))
```

```{r}
#| echo: false
#| output: false
sd(residuals_quad)
sd(residuals_cubic)
mean(residuals_quad^2)
mean(residuals_cubic^2)
```

**Results Interpretation**

## Part 3C Hetroskedasticity Testing and causality Discussion

**Causality vs causation**

While correlation indicates a relationship between two variables, it doesn't imply causation. In econometrics, it's a common pitfall to interpret correlation as causality. Panel data helps address this by allowing researchers to control for time-invariant factors and observe changes over time, which can provide stronger evidence for causal relationships.

Panel data analysis helps address endogeneity issues, such as omitted variable bias, which can lead to spurious correlation. By tracking the same units over time, it's possible to differentiate whether a relationship is genuinely causal or merely a correlation coinciding in time.

Overall, panel data analysis is a vital tool in econometrics for distinguishing between causality and correlation. By allowing for control over unobserved heterogeneity and providing a dynamic view of data over time, it offers a more nuanced and accurate understanding of the relationships between variables. This is crucial in econometric research, where the distinction between causality and mere correlation may have significant implications.

**Heteroskedasticity Testing**

```{r}
#| echo: false
#| output: false
#hetro
lm_01 <- lm(gini_n2 ~ GDP_per_capita, data = gini_filtered)
```

```{r}
#| echo: false
#| output: false
# Obtain fitted values and residuals from the model
fitted_values <- fitted(lm_01)
residuals <- resid(lm_01)

# Create the plot
plot(fitted_values, residuals, 
     xlab = "Fitted Values", 
     ylab = "Residuals", 
     main = "Residuals vs Fitted Values for Linear Model",
     pch = 20)
abline(h = 0, col = "blue", lwd = 2) # Add a horizontal line at 0
```

@@

The sets of disconnected residuals further out could indicate that there are distinct subgroups within our data that are behaving differently. It might suggest that the relationship between the variables differs across these groups or that there are influential outliers or leverage points affecting the model differently in these areas.

```{r}
#| echo: false
#| output: false
# Breusch-Pagan test for the original linear model
bptest_linear <- bptest(lm_01)

# Breusch-Pagan test for the logarithmic model
bptest_log <- bptest(log_model)

# Breusch-Pagan test for the quadratic model
bptest_quad <- bptest(quad_model)

# Output the test results
print(bptest_linear)
print(bptest_log)
print(bptest_quad)
```

```{r}
#| echo: false
#| output: false
# Calculate robust standard errors for the original linear model
coeftest_lm_01 <- coeftest(lm_01, vcov = vcovHC(lm_01, type = "HC"))

# Calculate robust standard errors for the logarithmic model
coeftest_log_model <- coeftest(log_model, vcov = vcovHC(log_model, type = "HC"))

# Calculate robust standard errors for the quadratic model
coeftest_quad_model <- coeftest(quad_model, vcov = vcovHC(quad_model, type = "HC"))

# Print out the results
print(coeftest_lm_01)
print(coeftest_log_model)
print(coeftest_quad_model)
```

## Part 3D Panel Estimates

@@

@lessmann2017 mention the use of a random-effects model to investigate the determinants of within-country changes in inequality. The random-effects model controls for several country-level fixed factors (national income, number of regions, and area) and fixed effects for various country groups [@lessmann2017]. The advantage of the random-effects model is that the expected value of the country-specific effect is zero, which means that there is no need to apply any arbitrary data imputation procedure for the missing intercepts [@lessmann2017]. However, this approach may come at the cost of founding the predictions on a slightly biased coefficient [@lessmann2017]. @lessmann2017 also notes that the major coefficient of interest is not sensitive to applying either a fixed-effects model or a random-effects model with additional country and region information [@lessmann2017].

# Discussion

>>>>

library(tidyverse)
library(tinytex)
library(dplyr)
library(ggplot2)
library(readxl)
library(magrittr)
library(vtable)
library(lubridate)
library(dineq)
library(huxtable)
library(plm)
library(sandwich)
library(lmtest)
```

@@

# Assignment 3: Alternative Functional Forms and Panel Estimates

## Testing Development Effects Across Subsets

### Subset Analysis

To begin the third assignment, we will explore if the effect of development and economic inequality is significantly different between different subsets in our dataset. For our assigned countries, we figured the best way to look at differences between them, is to examine the differences between our biggest country (France) compared to the rest of the countries. In order to compare the two different subsets, we will create a dummy variable. This dummy variable will help us with explaining qualitative values in the regression model.

Choosing France as a dummy variable amongst our group of countries could be justified based on several criteria. Firstly, France stands out as one of the largest economies in this group, both in terms of GDP and global economic influence. This distinction makes France a unique case compared to the smaller economies of Denmark, Portugal, Hungary, and Slovakia. Secondly, France's larger geographical area and population size provide different economic dynamics and complexities, which are not as pronounced in smaller and more homogenous countries. Thirdly, France's economy is more diversified compared to the other countries listed, which might have more specialized or less varied economic structures. This diversity can lead to different patterns in wealth distribution and economic development. Lastly, France's policies, particularly in social welfare and economic regulation, and its larger domestic market, might influence economic outcomes differently than in the smaller economies, where external trade and different policy contexts play a more significant role.

# Dummy variable
gini_filtered$France <- ifelse(gini_filtered$id_nuts0 == "FR", 1,0)
gini_filtered$Other <- ifelse(gini_filtered$id_nuts0 == "FR", 0,1)

# Regression analysis
gini_filtered <- gini_filtered
lmFR = lm(gini_n2 ~ GDP_per_capita, filter(gini_filtered, France == 1))
lmC = lm(gini_n2 ~ GDP_per_capita, filter(gini_filtered, France == 0))

huxreg(list("France" = lmFR, "All other countries" = lmC), statistics = c(N = "nobs", R2 = "r.squared", FStat = "statistic", PValue = "p.value"), note = "Note: {stars} T statistics in brackets.")
```

### Subset Analysis Discussion

For France, the regression model shows us a significant and positive relationship between GDP per capita and the Gini coefficient. The intercept is statistically significant, but negative. The positive coefficient of GDP per capita of 0.028 is highly significant with a p-value lower than 0.001; this suggests that when GDP per capita in France rises, then economic inequality rises correspondingly as well. We can also see this by looking at the R-squared of 0.637, indicating that around 63.7% of the variation in the economic inequality can be explained by changes in economic development (GDP per capita). To summarize our findings for France, we can see that economic growth in France can be associated with rising economic inequality, something that could possibly be due to a concentration of wealth in some regions (like Paris for example).

When looking at out other model with the other countries, we can see a different situation. The relationship between GDP per capita and Gini is not statistically significant. The model has a positive, but non-significant coefficient for GDP per capita, which can suggest that variations in this variable dosent have a significant impact on economic inequality. This is also shown by looking at the low R-squared of 0.004 \~ 0.4%, this may mean that GDP per capita only explains a rather small portion of the variance in inequality.

As we can see, there is a large gap between France and the other countries when it comes to the relationship between economic development and economic inequality.

## Exploring Alternative Functional Forms

In addition to the linear model, we can also use other different models in order to explain the relationship between regional development and economic inequality. By using these additional models, we can test different transformations of the variables in order to find the best representation of the data. Some of the models we can use are:

@@

In our analysis, we have chosen to focus on two models: the logarithmic transformation model and the quadratic model. The choice of these models is rooted in both their methodological robustness and their ability to capture the complex nature of the relationship between regional development and income inequality.

@@

# Comparing the different models with the linear model

# Linear model
linear_modelFR <- lm((gini_n2 ~ GDP_per_capita), filter(gini_filtered, France == 1))
linear_modelC <- lm((gini_n2 ~ GDP_per_capita), filter(gini_filtered, France == 0))

# Logarithmic model
log_modelFR <- lm(gini_n2 ~ log(GDP_per_capita), filter(gini_filtered, France == 1))
log_modelC <- lm(gini_n2 ~ log(GDP_per_capita), filter(gini_filtered, France == 0))

# Quadratic model
quadratic_modelFR <- lm(gini_n2 ~ log(GDP_per_capita) + I(GDP_per_capita^2), filter(gini_filtered, France == 1))
quadratic_modelC <- lm(gini_n2 ~ log(GDP_per_capita) + I(GDP_per_capita^2), filter(gini_filtered, France == 0))

huxreg(list("LinearFR" = linear_modelFR, "LinearC" = linear_modelC, "LogFR" = log_modelFR, "LogC" = log_modelC, "QuadraticFR" = quadratic_modelFR, "QuadraticC" = quadratic_modelC), statistics = c(N = "nobs", R2 = "r.squared", FStat = "statistic", PValue = "p.value"), note = "Note: {stars} T statistics in brackets.")
```

We have already seen in the linear regression model earlier that there is a significant positive correlation between GDP per capita and Gini for France, while its non-significant for the rest of the countries. In the logarithmic model, France also show that there is a positive relationship, with an R-squared of 0.490. The other countries still dosent have a significant relationship, and have a R-squared that is zero.

For the quadratic model, France have a positive coefficient for squared term of GDP per capita, something that can suggest a U-shaped relationship between the variables. The R-squared for France is 0.682, higher than the R-squared for the other models. The other countries also indicates a U-shaped relationship, and has a R-squared of 0.061; this means that the quadratic model is a better fit than the other models to explain the variance in income inequality.

#### Logarithmic Model

# Visaulization of Logarithmic model for France

france_data <- gini_filtered[gini_filtered$id_nuts0 == "FR", ]

france_data$predicted_gini_FR = predict(log_modelFR, newdata = france_data)

ggplot(france_data, aes(x = log(GDP_per_capita), y = gini_n2)) + 
  geom_point(aes(color = "Actual"), alpha = 0.5) + 
  geom_line(aes(y = predicted_gini_FR, color = "Predicted")) +
  labs(title = "Logarithmic Model for France: Predicted vs Actual Gini Coefficients",
       x = "Log of GDP per Capita",
       y = "Gini Coefficient",
       color = "Legend") +
  theme_minimal()
```

# Visaulization of Logarithmic model for the other countries

other_countries_data <- gini_filtered[gini_filtered$id_nuts0 != "FR", ]

other_countries_data$predicted_gini_C <- predict(log_modelC, newdata = other_countries_data)

ggplot(other_countries_data, aes(x = log(GDP_per_capita), y = gini_n2)) + 
  geom_point(aes(color = "Actual"), alpha = 0.5) + 
  geom_line(aes(y = predicted_gini_C, color = "Predicted")) +
  labs(title = "Logarithmic Model for Other Countries: Predicted vs Actual Gini Coefficients",
       x = "Log of GDP per Capita",
       y = "Gini Coefficient",
       color = "Legend") +
  theme_minimal()
```

In the plot for France, we can see a upward trend, which indicated that as the log of GDP per capita increases, the gini coefficient also increases, something that suggests higher income inequality. The data points are scattered around the predicted regression line, which goes upward. This pattern also supports the regression model that shows a significant positive realtionship between the variables. There are some extreme outliers, suggestion that some regions have a higher amount of economic activity (like Paris that is a economic center in France). This also shows that economic growth may lead to increased inequality because of the concentration of wealth in some regions.

The model for the other countries show that there is not a significant relationship between the variables. The data points also dosen't cluster around the predicted line, which shows that the log of GDP does not explain the variance in the Gini coefficient.

When analyzing both plots, it's clear that the relationship between economic development and income inequality behaves differently across these regions. The plot for France suggests that economic growth is associated with rising inequality, while the plot for the other countries indicates that economic growth has little to no effect on inequality

#### Quadratic Model

# Quadratic model for France

france_data$predicted_gini_FR = predict(quadratic_modelFR, newdata = france_data)

ggplot(france_data, aes(x = log(GDP_per_capita), y = gini_n2)) + 
  geom_point(aes(color = "Actual"), alpha = 0.5) + 
  geom_line(aes(y = predicted_gini_FR, color = "Predicted")) +
  labs(title = "Quadratic Model for France: Predicted vs Actual Gini Coefficients",
       x = "Log of GDP per Capita",
       y = "Gini Coefficient",
       color = "Legend") +
  theme_minimal()
```

# Quadratic model for the other countries

other_countries_data$predicted_gini_C <- predict(quadratic_modelC, newdata = other_countries_data)

ggplot(other_countries_data, aes(x = log(GDP_per_capita), y = gini_n2)) + 
  geom_point(aes(color = "Actual"), alpha = 0.5) + 
  geom_line(aes(y = predicted_gini_C, color = "Predicted")) +
  labs(title = "Quadratic Model for Other Countries: Predicted vs Actual Gini Coefficients",
       x = "Log of GDP per Capita",
       y = "Gini Coefficient",
       color = "Legend") +
  theme_minimal()
```

For France, the Gini coefficients are initially concentrated at lower levels of GDP per capita, presenting stability or a slight decrease in inequality, which then transitions into a sharp upward trend at higher GDP levels. This is indicative of an inverted U-shaped curve, a characteristic of the Kuznets curve hypothesis, suggesting that inequality escalates significantly with further economic growth [@ota2017]. The quadratic model appears to fit the lower and middle range of the data well, yet it deviates from the actual data points at the higher end of GDP per capita, signaling that other factors may come into play as the economy grows.

The quadratic model for the other countries shows a more subtle U-shaped relationship, with the initial part of the curve being relatively flat. This indicates that changes in GDP per capita have a limited effect on income inequality at first. However, a steep increase is observed at the higher end of GDP per capita, which may be attributed to outliers or specific country conditions not captured by the model.

Incorporating these observations, both plots still signify a non-linear relationship between GDP per capita and income inequality, but with varying patterns and intensities between France and the other countries. The pronounced curve for France supports a stronger Kuznets curve effect, while for the other countries, the effect is less pronounced and the connection between economic growth and inequality appears to be weaker and more influenced by external or unmodeled factors.

### Results Interpretation

The linear model, while providing a significant fit for France, falls short for the other countries, suggesting that the economic inequality's relationship to GDP per capita may not be linear or might be influenced by factors not captured in a simple linear model. The logarithmic model's reduced explanatory power compared to the linear model for France suggests that the relationship between GDP and inequality may not be strictly proportional across all levels of GDP per capita.

The quadratic model's U-shaped curve implies that as countries develop, inequality may first decrease and then increase, supporting the Kuznets curve hypothesis.

In conclusion, while the linear model provides a baseline understanding of the relationship between GDP per capita and income inequality, the logarithmic and quadratic models offer more nuanced insights that can lead to a deeper understanding of the underlying economic mechanisms. These alternative models highlight the importance of considering non-linear dynamics when analyzing economic relationships.

## Heteroskedasticity Testing and Causality Discussion

### Heteroskedasticity Testing

# Breusch-Pagan test for the original linear model
bptest_linearFR <- bptest(linear_modelFR)
bptest_linearC <- bptest(linear_modelC)

# Breusch-Pagan test for the logarithmic model
bptest_logFR <- bptest(log_modelFR)
bptest_logC <- bptest(log_modelC)

# Breusch-Pagan test for the quadratic model
bptest_quadFR <- bptest(quadratic_modelFR)
bptest_quadC <- bptest(quadratic_modelC)

# Output of test results
print(bptest_linearFR)
print(bptest_linearC)
print(bptest_logFR)
print(bptest_logC)
print(bptest_quadFR)
print(bptest_quadC)
```

The Breusch-Pagan test results suggest that the linear and logarithmic models for the other countries and the quadratic models for both France and the other countries exhibit heteroskedasticity. This could have implications for the standard errors and confidence intervals of the coefficients, potentially leading to incorrect inferences about the significance of predictors. The linear model for France does not appear to suffer from this issue.

Given these findings, it may be necessary to consider heteroskedasticity-robust standard errors or to transform the data or model specification to address this issue. It is essential to correct for heteroskedasticity to ensure the reliability of the regression analysis.

# Residuals vs fitted values for linear model, all countries combined (including France)

lm_01 <- lm(gini_n2 ~ GDP_per_capita, data = gini_filtered)

# Obtaining fitted values and residuals from the model
fitted_values <- fitted(lm_01)
residuals <- resid(lm_01)

plot(fitted_values, residuals, 
     xlab = "Fitted Values", 
     ylab = "Residuals", 
     main = "Residuals vs Fitted Values for Linear Model",
     pch = 20)
abline(h = 0, col = "blue", lwd = 2)
```

@@

### Causality Discussion:

The Breusch-Pagan tests have confirmed the presence of heteroskedasticity in most of our models, especially for the other countries. This suggests that the assumption of homoscedasticity is violated in these models. Heteroskedasticity and patterns in the residuals can lead to inefficient estimates and undermine the causal interpretation of the models. When the error variance changes across observations, the standard errors of the coefficient estimates may be biased, leading to incorrect conclusions about the significance of predictors.

The best strategies to address these issues might be to use heteroskedasticity-robust standard errors (White's standard errors), apply transformations to the dependent variable, or using weighted least squares (WLS). These strategies can help mitigate issues and lead to more robust conclusions.

## Panel Estimates

@@

@lessmann2017 mention the use of a random-effects model to investigate the determinants of within-country changes in inequality. The random-effects model controls for several country-level fixed factors (national income, number of regions, and area) and fixed effects for various country groups [@lessmann2017]. The advantage of the random-effects model is that the expected value of the country-specific effect is zero, which means that there is no need to apply any arbitrary data imputation procedure for the missing intercepts [@lessmann2017]. However, this approach may come at the cost of founding the predictions on a slightly biased coefficient [@lessmann2017]. @lessmann2017 also notes that the major coefficient of interest is not sensitive to applying either a fixed-effects model or a random-effects model with additional country and region information.

### Panel Estimation Task:

# Panel estiamtion

plm1 <- plm(gini_n2 ~ GDP_per_capita + log(GDP_per_capita), data = gini_filtered, index = c("id_nuts0"), model = "within",effect = "twoway") |> 
  coeftest(vcov. = vcovHC, type = "HC1", save = TRUE)

plm2 <- plm(gini_n2 ~ GDP_per_capita + log(GDP_per_capita), data = gini_filtered, index = c("year"), model = "within",effect = "twoway") |> 
  coeftest(vcov. = vcovHC, type = "HC1", save = TRUE)

plm3 <- plm(gini_n2 ~ GDP_per_capita + log(GDP_per_capita), data = gini_filtered, index = c("id_nuts2"), model = "within",effect = "twoway") |> 
  coeftest(vcov. = vcovHC, type = "HC1", save = TRUE)

plm4 <- plm(gini_n2 ~ GDP_per_capita + log(GDP_per_capita), data = gini_filtered, index = c("year","id_nuts2"), model = "within",effect = "twoway") |> 
  coeftest(vcov. = vcovHC, type = "HC1", save = TRUE)

huxreg(plm1, plm2, plm3, plm4, statistics = c("nobs","r.squared","adj.r.squared", "statistic", "p.value"), 
       stars = c("*" = 0.1, "**" = 0.05, "***" = 0.01),
       note = "Note): {stars} T statistics in brackets.")
```

### Panel Estimation Analysis

### Panel Estimation Discussion
